---
title: "MSDS 6306: Introduction to Data Science - Live session Unit 01 Assignment"
output: word_document
---
### 1)
a. log(10) = ```r log(10)```
b. ?log(): description says that log() default is the natural log. Using base 10: log(10, base = 10) = ```r log(10, base = 10)```
c. Log(-10) = ```r log(-10)``` Cannot take the log of a negative number. The log curve is asymptotic to negative infinity as x approaches zero(log(0) = ```r log(0)```
d. sqrt(4) = ```r sqrt(4)```

### 2)
a. 
```{r}
rNormVector <- rnorm(15)
mean(rNormVector)
sd(rNormVector)
```

b. 
```{r}
rNormVector <- rnorm(15,mean = 10,sd = 2)
mean(rNormVector)
sd(rNormVector)
```

c. The values are randomly sampled fromt he distribution so the exact values will not match. As the sample size increases the mean will get closer to the actual mean.

### 3)

```{r}
indWeight <-  c(60, 72, 57, 90, 95, 72)
indHeight <- c(1.80, 1.85, 1.72, 1.90, 1.74, 1.91) 
plot(indWeight, indHeight) # Weight and height would seem to be positivly related
indBMI <- indWeight / sqrt(indHeight)
sum(mean(indWeight) - indWeight)

```

### 4)

```{r}
brychan <- data.frame(
  area = c("computer programming", "math", "statistics", "machine learning", "domain expertise", 
           "communication and \npresentation skills", "data visualization"),
  rank = c(3, 4, 3, 2, 4, 2, 4)
  )
par(mar = c(10,2,2,2))
barplot(brychan$rank, names.arg = brychan$area,las=2)


```


### 5)


